Timeliness of security updates for Android

### 2014-10-28 securityupdates.tex
summarise experiment 2 in introduction to Experiments

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root equivalent vulnerabilities on average. Nexus devices are better than others, \emph{\daSecScoreBestmanufacturer} to be the best manufacturer and \emph{\daSecScoreBestoperator} to be the best network operator and modelling the uptake of new versions of Android. \todo{summarise experiment 2}
%\todo{comparison of nexus update rates with iOS}
We conducted four experiments examining the behaviour of the Android ecosystem as a whole (\S\ref{sec:exp:android_ecosystem}), updates reaching particular devices (\S\ref{sec:exp:device_updates}), comparisons between different manufacturers and operators (\S\ref{sec:exp:security_score}) and model how long it will take for an update to be fixed once an update is released (\S\ref{sec:exp:predicting_distributions}).

@@

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frvh_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version\todo{make line of best fit thicker, I think the drops to 0 at the end of each version are erroneous}}
 \label{fig:frvh_os_versions}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frms_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version}
 \label{fig:frms_os_versions}
\end{figure}

>>>>

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root equivalent vulnerabilities on average.
On average only \daUpdatesPerYear\ updates reach a device each year and \daPercUpdatesDowngrades\ of version changes are downgrades to older versions.
Nexus devices are better than others, \emph{\daSecScoreBestmanufacturer} to be the best manufacturer and \emph{\daSecScoreBestoperator} to be the best network operator and modelling the uptake of new versions of Android.
%\todo{comparison of nexus update rates with iOS}
We conducted four experiments examining the behaviour of the Android ecosystem as a whole (\S\ref{sec:exp:android_ecosystem}), updates reaching particular devices (\S\ref{sec:exp:device_updates}), comparisons between different manufacturers and operators (\S\ref{sec:exp:security_score}) and model how long it will take for an update to be fixed once an update is released (\S\ref{sec:exp:predicting_distributions}).

@@

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frvh_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version}
 \label{fig:frvh_os_versions}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frms_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version}
 \label{fig:frms_os_versions}
\end{figure}
